### 2019-05-14 Manuscript/Manuscript.tex
v7 commit

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=\textwidth]{Manuscript/Figures/LIP_Map.pdf}
	\caption{Map of current extent of volcanic lithologies associated with LIPs that erupted between 520~Ma and the present, as well as the estimates of the initial LIP extent used in the area analysis (modified slightly from \citealp{Ernst2017a} and \citealp{Ernst2019a} to ensure that all currently exposed volcanic lithologies are encapsulated by the initial LIP area polygons).}
	\label{fig:LIP_map}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.6\textwidth]{Manuscript/Figures/LIP_Preservation.pdf}
	\caption{LIP erosion through time. The ratio of estimates of the present-day area to that of the original area are shown for 19 basaltic LIPs. An exponential fit is made to the 13 basaltic LIPs that are interpreted to not have been buried after emplacement (Table \ref{tab:LIPs}), which yields a half-life of $\sim$36~Myr. RMSE = root mean square error.}
	\label{fig:LIP_preservation}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=\textwidth]{Manuscript/Figures/Climatology.pdf}
	\caption{Zonally averaged modern climatological data used to define the tropical rain belt. The global precipitation \citep{Kalnay1996a} and precipitation minus evaporation \citep{Trenberth2011a} data include land and ocean pixels, whereas global temperature data \citep{Kalnay1996a} are from land only, and runoff data \citep{Fekete1999a} are from land only excluding Antarctica. The peak in runoff $\sim$-50\textdegree\xspace is due to anomalously high orographically-induced runoff in the southern Andes, which represents almost all of the land in that latitude belt. Temperature data for Antarctica are off scale. Precipitation, precipitation minus evaporation, and runoff all increase sharply between $\pm$10\textdegree\xspace and $\pm$15\textdegree\xspace.}
	\label{fig:Climatology}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.9\textwidth]{Manuscript/Figures/LIP_Areas.pdf}
	\caption{\textbf{A)} LIPs included in this analysis. The size of each circle reflects the initial area estimate of each LIP. The + indicates the timing and absolute paleolatitude of the centroid of each LIP at the time of emplacement. Car.-Col. = Caribbean-Colombian. \textbf{B)} Total LIP area through time for the different post-emplacent scenarios. Only the `no decay' scenario excludes pre-Phanerozoic LIPs. \textbf{C)} Tropical LIP area through time for the different post-emplacement scenarios. The arrows to the right indicate reconstructed tropical LIP area at the time of emplacement for the ca. 720 and 1109~Ma Franklin and Umkondo LIPs. The triangles show the paleogeographic reconstruction times in Fig. \ref{fig:Reconstruction_Snapshots}. \textbf{D)} Contour plot showing the latitudinal distribution of LIP area for the preferred post-emplacement model. \textbf{E)} Latitudinal extent of land ice away from the poles \citep{Macdonald2019a} and compilation of \textit{p}CO$_{2}$ proxies \citep{Foster2017a} (\textit{p}CO$_{2}$ y-axis reversed, and in log-scale). Error bars indicate standardized uncertainties, and grey bands indicate 68 and 95\% confidence intervals for Monte Carlo resampled LOESS fits to the \textit{p}CO$_{2}$ proxy data \citep{Foster2017a}. Note that there are \textit{p}CO$_{2}$ proxy estimates \textless100~ppm that are cut off in this plot.}
	\label{fig:LIP_Areas}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=\textwidth]{Manuscript/Figures/Reconstruction_Snapshots.pdf}
	\caption{Paleogeographic reconstructions for times that correspond to peaks of LIP area in the tropics (Fig. \ref{fig:LIP_Areas}C). The opacity of LIP polygons indicates their parameterized remaining area at the time of the reconstruction as a percentage of initial LIP area, under the preferred post-emplacement scenario of `t$_{1/2}$ = 36~Myr + 50\% burial'.}
	\label{fig:Reconstruction_Snapshots}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.85\textwidth]{Manuscript/Figures/overlap_correlation_cropped.pdf}
	\caption{The \% overlap and Pearson correlation coefficients between LIP area and the actual ice-extent record are shown with circles. These values are compared to histograms that show the range of values that arise when comparing the LIP area record to glacial intervals that have been shifted randomly in time 100,000 times. The fraction of randomly timed glacial interval simulations that correlate/overlap better with LIP area than the actual ice-extent record is the p-value shown in Table \ref{tab:stats}.}
	\label{fig:LIP_correlation}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.9\textwidth]{Manuscript/Figures/Continent_Areas.pdf}
	\caption{\textbf{A)} Total continental area through time. In the paleogeographic model used in this study, tectonic units \citep{Torsvik2016a} are progressively added to the model, leading to a net increase in total continental area in the model of $\sim$33\% over the Phanerozoic. However, estimates of continental crust growth (e.g. \citealp{Pujol2013a}) suggest that continental area was roughly constant through the Phanerozoic. We therefore normalize the total continental area curve in our model by assuming a fixed continental area through the Phanerozoic. \textbf{B)} Tropical continental area through time. We normalize the tropical continental area curve using the normalization ratio implied in (A). \textbf{C)} Contour plot showing the latitudinal distribution of continental area. \textbf{D)} Latitudinal extent of land ice away from the poles \citep{Macdonald2019a}.}
	\label{fig:Continent_Areas}
\end{center}
\end{figure}

>>>>

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=\textwidth]{./Figures/LIP_Map.pdf}
	\caption{Map of current extent of volcanic lithologies associated with LIPs that erupted between 520~Ma and the present, as well as the estimates of the initial LIP extent used in the area analysis (modified slightly from \citealp{Ernst2017a} and \citealp{Ernst2019a} to ensure that all currently exposed volcanic lithologies are encapsulated by the initial LIP area polygons).}
	\label{fig:LIP_map}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.6\textwidth]{./Figures/LIP_Preservation.pdf}
	\caption{LIP erosion through time. The ratio of estimates of the present-day area to that of the original area are shown for 19 basaltic LIPs. An exponential fit is made to the 13 basaltic LIPs that are interpreted to not have been buried after emplacement (Table \ref{tab:LIPs}), which yields a half-life of $\sim$36~Myr. RMSE = root mean square error.}
	\label{fig:LIP_preservation}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=\textwidth]{./Figures/Climatology.pdf}
	\caption{Zonally averaged modern climatological data used to define the tropical rain belt. The global precipitation \citep{Kalnay1996a} and precipitation minus evaporation \citep{Trenberth2011a} data include land and ocean pixels, whereas global temperature data \citep{Kalnay1996a} are from land only, and runoff data \citep{Fekete1999a} are from land only excluding Antarctica. The peak in runoff $\sim$-50\textdegree\xspace is due to anomalously high orographically-induced runoff in the southern Andes, which represents almost all of the land in that latitude belt. Temperature data for Antarctica are off scale. Precipitation, precipitation minus evaporation, and runoff all increase sharply between $\pm$10\textdegree\xspace and $\pm$15\textdegree\xspace.}
	\label{fig:Climatology}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.9\textwidth]{./Figures/LIP_Areas.pdf}
	\caption{\textbf{A)} LIPs included in this analysis. The size of each circle reflects the initial area estimate of each LIP. The + indicates the timing and absolute paleolatitude of the centroid of each LIP at the time of emplacement. Car.-Col. = Caribbean-Colombian. \textbf{B)} Total LIP area through time for the different post-emplacent scenarios. Only the `no decay' scenario excludes pre-Phanerozoic LIPs. \textbf{C)} Tropical LIP area through time for the different post-emplacement scenarios. The arrows to the right indicate reconstructed tropical LIP area at the time of emplacement for the ca. 720 and 1109~Ma Franklin and Umkondo LIPs. The triangles show the paleogeographic reconstruction times in Fig. \ref{fig:Reconstruction_Snapshots}. \textbf{D)} Contour plot showing the latitudinal distribution of LIP area for the preferred post-emplacement model. \textbf{E)} Latitudinal extent of land ice away from the poles \citep{Macdonald2019a} and compilation of \textit{p}CO$_{2}$ proxies \citep{Foster2017a} (\textit{p}CO$_{2}$ y-axis reversed, and in log-scale). Error bars indicate standardized uncertainties, and grey bands indicate 68 and 95\% confidence intervals for Monte Carlo resampled LOESS fits to the \textit{p}CO$_{2}$ proxy data \citep{Foster2017a}. Note that there are \textit{p}CO$_{2}$ proxy estimates \textless100~ppm that are cut off in this plot.}
	\label{fig:LIP_Areas}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=\textwidth]{./Figures/Reconstruction_Snapshots.pdf}
	\caption{Paleogeographic reconstructions for times that correspond to peaks of LIP area in the tropics (Fig. \ref{fig:LIP_Areas}C). The opacity of LIP polygons indicates their parameterized remaining area at the time of the reconstruction as a percentage of initial LIP area, under the preferred post-emplacement scenario of `t$_{1/2}$ = 36~Myr + 50\% burial'.}
	\label{fig:Reconstruction_Snapshots}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.85\textwidth]{./Figures/overlap_correlation_cropped.pdf}
	\caption{The \% overlap and Pearson correlation coefficients between LIP area and the actual ice-extent record are shown with circles. These values are compared to histograms that show the range of values that arise when comparing the LIP area record to glacial intervals that have been shifted randomly in time 100,000 times. The fraction of randomly timed glacial interval simulations that correlate/overlap better with LIP area than the actual ice-extent record is the p-value shown in Table \ref{tab:stats}.}
	\label{fig:LIP_correlation}
\end{center}
\end{figure}

\begin{figure}[h!]
\begin{center}
	\includegraphics[width=0.9\textwidth]{./Figures/Continent_Areas.pdf}
	\caption{\textbf{A)} Total continental area through time. In the paleogeographic model used in this study, tectonic units \citep{Torsvik2016a} are progressively added to the model, leading to a net increase in total continental area in the model of $\sim$33\% over the Phanerozoic. However, estimates of continental crust growth (e.g. \citealp{Pujol2013a}) suggest that continental area was roughly constant through the Phanerozoic. We therefore normalize the total continental area curve in our model by assuming a fixed continental area through the Phanerozoic. \textbf{B)} Tropical continental area through time. We normalize the tropical continental area curve using the normalization ratio implied in (A). \textbf{C)} Contour plot showing the latitudinal distribution of continental area. \textbf{D)} Latitudinal extent of land ice away from the poles \citep{Macdonald2019a}.}
	\label{fig:Continent_Areas}
\end{center}
\end{figure}
